---
title: "Stock portfolio simulation"
author: "Rohan Agarwal"
date: '2022-08-31'
output: html_document
---
## Using data on seven stocks from Yahoo! Finance to graph stock prices. 
The following stocks were used in this analysis: 
- Apple
- Amazon
- Google 
- Meta 
- Microsoft 
- Netflix 
- Uber \n
The data range is from March 03, 2022 to August 30, 2022. \n


```{r setup and libraries}
# Loading the required packages 
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/HFT/Stock_market_program /Stock-Price-Graphing")
library(haven)
library(Hmisc)
library(stargazer)
library(dplyr)
library (zoo)
library(readr)
library(ggplot2)
library (TSstudio)
```

## Loading and cleaning the data \n
The data from Yahoo! Finance was downloaded as 7 separate .CSV files. \n
It will be loaded as seven separate data frames and then cleaned using the **zoo** package. 

```{r dataset}

# First, we will load 7 data frames containing the data downloaded from Yahoo, which has daily highs, lows, and closing prices 
# for the seven stocks we are interested in. 
aapl.df <- read.csv("AAPL.csv", header = TRUE, stringsAsFactors = FALSE)
amzn.df <- read.csv("AMZN.csv", header = TRUE, stringsAsFactors = FALSE)
goog.df <- read.csv("GOOG.csv", header = TRUE, stringsAsFactors = FALSE)
meta.df <- read.csv("META.csv", header = TRUE, stringsAsFactors = FALSE)
msft.df <- read.csv("MSFT.csv", header = TRUE, stringsAsFactors = FALSE)
nflx.df <- read.csv("NFLX.csv", header = TRUE, stringsAsFactors = FALSE)
uber.df <- read.csv("UBER.csv", header = TRUE, stringsAsFactors = FALSE)

# Now, we subset the data so that only the adjusted closing price is retained. 

aapl.cl.df <- subset(aapl.df, select = c(Date, Close))
amzn.cl.df <- subset(amzn.df, select = c(Date, Close))
goog.cl.df <- subset(goog.df, select = c(Date, Close))
meta.cl.df <- subset(meta.df, select = c(Date, Close))
msft.cl.df <- subset(msft.df, select = c(Date, Close))
nflx.cl.df <- subset(nflx.df, select = c(Date, Close))
uber.cl.df <- subset(uber.df, select = c(Date, Close))

# Reassigning the column names so that there is no confusion after the data is merged. 
colnames(aapl.cl.df)<- c("Date", "Apple adjusted closing share price")
colnames(amzn.cl.df)<- c("Date", "Amazon adjusted closing share price")
colnames(goog.cl.df)<- c("Date", "Google adjusted closing share price")
colnames(meta.cl.df)<- c("Date", "Meta adjusted closing share price")
colnames(msft.cl.df)<- c("Date", "Microsoft adjusted closing share price")
colnames(nflx.cl.df)<- c("Date", "Netflix adjusted closing share price")
colnames(uber.cl.df)<- c("Date", "Uber adjusted closing share price")

```

```{r}

# We use the **zoo** package designed to handle arbitrarily ordered time index time-series data. 
td = as.Date(aapl.cl.df$Date, format = "%Y-%m-%d")

aapl.z <- zoo(x = aapl.cl.df$`Apple adjusted closing share price`, order.by=td)
amzn.z <- zoo(x = amzn.cl.df$`Amazon adjusted closing share price`, order.by=td)
goog.z <- zoo(x = goog.cl.df$`Google adjusted closing share price`, order.by=td)
meta.z <- zoo(x = meta.cl.df$`Meta adjusted closing share price`, order.by=td)
msft.z <- zoo(x = msft.cl.df$`Microsoft adjusted closing share price`, order.by=td)
nflx.z <- zoo(x = nflx.cl.df$`Netflix adjusted closing share price`, order.by=td)
uber.z <- zoo(x = uber.cl.df$`Uber adjusted closing share price`, order.by=td)
head(aapl.z)
# Merging the seven *zoo* objects into one
stocks.z <- cbind(aapl.z, amzn.z, goog.z, meta.z, msft.z, nflx.z, uber.z)

#Changing the names of the columns 
colnames(stocks.z)<- c("Apple", "Amazon", "Google", "Meta", "Microsoft", "Netflix", "Uber")
head(stocks.z)
# Plotting the stocks to get an idea of what stock price fluctuations were like. 
plot (stocks.z, plot.type = 'single',
      col = c(1:7),
      xlab = "Dates",
      ylab = "Daily closing stock prices for seven tech companies", 
      sub = "Year: 2022",
      )
legend("topright", inset = c(0,0), legend = c("Apple", "Amazon", "Google", "Meta", "Microsoft", "Netflix", "Uber"), cex = 0.5, 
       col = c(1:7),
       lty = 1, bty = "n"
)
```
